### 2013-08-02 Tex/chapters/results.tex
Collapse Besipiele nicht nur für sigma = 0

    averaged over all determined values. Fig. \ref{fig:gettingCrit2}\subref{sfig:gettingCrit:s_0_sus}\subref{sfig:gettingCrit:collapse_s_0_sus}

@@

    Analogical fig. \ref{fig:gettingCrit2}\subref{sfig:gettingCrit:s_0_meanM}\subref{sfig:gettingCrit:collapse_s_0_meanM}

@@

            \label{sfig:gettingCrit:s_0_sus}
            \includegraphics[width=0.47\textwidth]{plots/s_0_sus}

@@

            \label{sfig:gettingCrit:collapse_s_0_sus}
            \includegraphics[width=0.47\textwidth]{plots/collapse_s_0_sus}

@@

            \label{sfig:gettingCrit:s_0_meanM}
            \includegraphics[width=0.47\textwidth]{plots/s_0_meanM}

@@

            \label{sfig:gettingCrit:collapse_s_0_meanM}
            \includegraphics[width=0.47\textwidth]{plots/collapse_s_0_meanM}

@@

            \subref{sfig:gettingCrit:s_0_sus} The susceptibility \(\chi\)
            \subref{sfig:gettingCrit:collapse_s_0_sus} collapsed by finite
                size scaling\\
            \subref{sfig:gettingCrit:s_0_meanM} The mean absolute magnetization \(\avg{\abs{m}}\)
            \subref{sfig:gettingCrit:collapse_s_0_meanM} collapsed by finite
                size scaling

>>>>

    averaged over all determined values. Fig. \ref{fig:gettingCrit2}\subref{sfig:gettingCrit:s_1_sus}\subref{sfig:gettingCrit:collapse_s_1_sus}

@@

    Analogical fig. \ref{fig:gettingCrit2}\subref{sfig:gettingCrit:s_1_meanM}\subref{sfig:gettingCrit:collapse_s_1_meanM}

@@

            \label{sfig:gettingCrit:s_1_sus}
            \includegraphics[width=0.47\textwidth]{plots/s_1_sus}

@@

            \label{sfig:gettingCrit:collapse_s_1_sus}
            \includegraphics[width=0.47\textwidth]{plots/collapse_s_1_sus}

@@

            \label{sfig:gettingCrit:s_1_meanM}
            \includegraphics[width=0.47\textwidth]{plots/s_1_meanM}

@@

            \label{sfig:gettingCrit:collapse_s_1_meanM}
            \includegraphics[width=0.47\textwidth]{plots/collapse_s_1_meanM}

@@

            \subref{sfig:gettingCrit:s_1_sus} The susceptibility \(\chi\)
                of an Ising model on an RNG \(\sigma=1\)\\
            \subref{sfig:gettingCrit:collapse_s_1_sus} collapsed by finite
                size scaling (for error estimates see \ref{tab:critExp})\\
            \subref{sfig:gettingCrit:s_1_meanM} The mean absolute magnetization \(\avg{\abs{m}}\)
                of an Ising model on an GG \(\sigma=1\)\\
            \subref{sfig:gettingCrit:collapse_s_1_meanM} collapsed by finite
                size scaling (for error estimates see \ref{tab:critExp})
